DynaProg for Scala

### 2013-01-10 docs/report/introduction.tex
Nits in report.
More report.

As the Scala programming language is initially developed by the LAMP, it seems natural to use it as host language for our project, however, we would list its features that makes it an interesting development language for this project:\ul
\item The functional programming style and syntactic sugar offered by Scala allows concise writing of implementation, analysis and transformations of our DSL, which would have been much more complex and tiresome in an imperative language like C.
\item Scala is largely adopted in the industry, which makes both the adoption of related project easier and offer a steeper learning curve to their potential users.
\item Finally, through the Java VM and JNI interface, Scala offers the possibility to load dynamically external libraries, to leverage best underlying hardware by mixing with CUDA kernels to obtain optimal performance.
\ule

>>>>

As the Scala \cite{scala} programming language is initially developed by the LAMP, it seems natural to use it as host language for our project, however, we would list some of its features \cite{scala_api} that makes it an interesting development language for this project:\ul
\item The functional programming style and syntactic sugar offered by Scala allows concise writing of implementation, analysis and transformations of our DSL, which would have been much more complex and tiresome in an imperative language like C.
\item Scala is largely adopted in the industry, which makes both the adoption of related project easier and offer a steeper learning curve to their potential users.
\item Finally, through the Java VM and JNI interface, Scala offers the possibility to load dynamically external libraries, to leverage best underlying hardware by mixing with CUDA kernels to obtain optimal performance.
\ule

### 2013-01-10 docs/report/problems.tex
More report.

Although the polygon triangulation problem can be solved with a regular triangular matrix and we have not found real problem requiring a parallelogram matrix, we still present this version in the analysis part of the project, which could be justified for cyclic problems that require dynamic programming for each unfolding position (that is for all position in the circular structure, break the cycle at this position, and solve the dynamic programming problem on the resulting flattened sequence). For example, one could be interested in finding the longest subsequence verifying some property in a cycle, such that the subsequence score changes if it is rotated.

\ole

>>>>

Although the polygon triangulation problem can be solved with a regular triangular matrix and we have not found real problem requiring a parallelogram matrix, we still present this version in the analysis part of the project, which could be justified for cyclic problems that require dynamic programming for each unfolding position (that is for all position in the circular structure, break the cycle at this position, and solve the dynamic programming problem on the resulting flattened sequence). For example, one could be interested in finding the longest subsequence verifying some property in a cycle, such that the subsequence score changes if it is rotated.
\ole

\subsection{Related work}
Work related to dynamic programming can be separated in two categories: ad-hoc implementations and grammar-based implementations. Grammar-based dynamic programming was initiated sparked by \cite{adp_discipline} and implemented as a Haskell DSL \cite{adp}. To overcome performance issues, multiple solutions were devised: converting the grammar to C or CUDA code \cite{adp_gpu} or using loop fusion to improve Haskell performance \cite{adp_fusion}. Ultimately, the dynamic programming algebra and grammar were formalized into an external DSL 
and ad-hoc compiler

Related work is a DSL embedded in Haskell \cite{adp} with possible conversion to CUDA code \cite{adp_gpu}, a compiler for a dynamic programming external DSL into C code \cite{gapc} or ad-hoc CUDA implementations for specific problem classes \cite{swat_mega}, \cite{gpu_atlp}.

### 2013-01-10 docs/report/report.tex
Nits.
More report.

Existing work is a DSL embedded in Haskell \cite{adp} with possible conversion to CUDA code \cite{adp_gpu}, a compiler for a dynamic programming external DSL into C code \cite{gapc} or ad-hoc CUDA implementations for specific problem classes \cite{swat_mega}, \cite{gpu_atlp}.
% XXX: How we compare to other, how to evaluate
% Benchmark => prove by evaluation intro statements

@@

\input{introduction}
\input{problems}
\input{design}
\input{implementation}
\section{Benchmarks}
\subsection{Java parsers}
{\color{red}
MatrixMult-512, Mac+JDK7\ul
\item Original: 24.937 sec / 24.658 sec
\item Optimized concatenation: 19.329 sec / 18.924 sec
\item Tabulation as arrays+inline: 15.068 sec / 14.900 sec
\ule}

>>>>

Related work is a DSL embedded in Haskell \cite{adp} with possible conversion to CUDA code \cite{adp_gpu}, a compiler for a dynamic programming external DSL into C code \cite{gapc} or ad-hoc CUDA implementations for specific problem classes \cite{swat_mega}, \cite{gpu_atlp}.
% XXX: How we compare to other, how to evaluate
% Benchmark => prove by evaluation intro statements

@@

\input{introduction}
\input{problems}
\input{design}
\input{implementation}
\section{Benchmarks}
\subsection{Java parsers}
{\color{red}
MatrixMult-512, Mac+JDK7\ul
\item Original: 24.937 sec / 24.658 sec
\item Optimized concatenation: 19.329 sec / 18.924 sec
\item Tabulation as arrays+inline: 14.976 sec / 14.849 sec
\ule}
